--- 
title: "A Minimal Book Example"
author: "Yihui Xie"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

<!--chapter:end:index.Rmd-->

# The Yokoyama Lab {#the-lab}

Yokoyama Lab Overview 

## Yokoyama Lab Mission {#lab-mission}



## Our Philosophy {#lab-philosophy}



## Our Research


## Our Core Values {#lab-values}

The way we conduct ourselves is a critical part of how we conduct science. Lab members will strive to uphold the following values:

* **Integrity**: Like many things in the world, science is built on trust and honesty. We will pursue rigorous and transparent research, ensuring our work is credible and reliable.

* **Humility**: By accepting that we may not decidedly know or understand everything, we are open to new perspectives. We are willing to admit we made mistakes and share what we have learned from them.

* **Kindness**: Science involves skepticism and criticism, but that does not mean it cannot be done with care and empathy. We hope to be respectful members of the scientific community, being considerate and supportive to our colleagues at all levels. 

* **Diversity**: Science should reflect the vast perspectives, experiences and people that exist in the world. Our lab hopes to be inclusive to all, and promote equity throughout science.

## Our Location






<!--chapter:end:01-about.Rmd-->

# Lab Culture {#lab-culture}

This chapter describes the structure and culture within the PALM Lab. The goal is to be clear about expectations for the members of the lab (ones that I have, as well as for each other) and importantly for myself.

> _This section aims to provide a picture of what mentoring and working with me will be like in the PALM Lab. It will continually be in-progress, shaped by (and including) feedback from lab members and others alike. -- William_

## Lab Environment {#lab-environment}


## Work Expectations {#lab-work}

### Time Off {#lab-timeoff}

### Communication Expectations {#lab-communication}

## Mentorship {#lab-mentorship}

## Resolving Conflicts {#conflicts}

<!--chapter:end:02-lab-culture.Rmd-->

# Research Policies

## Academic Integrity

## Authorship {#authorship}

## Open Science {#open-science}

### Sharing experiment code and data

### Preprints and conference presentations


<!--chapter:end:03-research-policies.Rmd-->

# Lab Resources


## Required Tools



## Recommended

## Optional

<!--chapter:end:04-resources.Rmd-->

# Yokoyama Lab Onboarding {#getting-started}


## Before you Join

## First Week Tasks

## First Six Months


<!--chapter:end:05-getting-started.Rmd-->

# Miscellaneous

## Collaborators

## Additional resources {#extra-resources}



<!--chapter:end:06-miscellaneous.Rmd-->

`r if (knitr::is_html_output()) '
# References {-}

'`

<!--chapter:end:07-references.Rmd-->

